Paper \#ZW10157

### 2019-01-31 paper/submission/ZW10157-response-1.tex
added Linda's edit to TBA section

{\bf Our response:} {\color{blue} 
	Several changes were made in the paper to address this concern. 
	 abstract to explain the AWA problem. 
	Here is the new abstract in it's entirety:

@@

>>>>

{\bf Our response:} {\color{blue} 
	Several changes were made in the paper to address this concern. 
	The abstract was edited to explain the AWA problem. 
	Here is the new abstract in it's entirety:

@@

The following information was added on lines 479-496:

Overall this solution is satisfactory, and meets all requirements for the new TBA beamline at the AWA.
A Power Extractor and Transfer Structure (PETS) will be located after the septum and quadrupoles in Fig. 7.
This device is putting the tightest constraints on the beam parameters.  
The aperture diameter is 17.6 mm and bunch length should be below 2 mm
to facilitate large power extraction [new ref here].

The optimization results shown here were used in part to meet all TBA requirements. 
After adjustments to include 3D rf field maps and CSR in the dipoles[new ref here] 
the max beamsizes at the PETS location were below 10 mm with a bunch length of rmsz=1.6 mm. 
Although the simulation results at the PETS location cannot yet be verified, since the beamline is not yet completely installed, 
some checks have been possible for the partially completed beamline.  
Simulations of the partial beamline have been done.
For example, beam images were taken on the YAG screen located downstream of the kicker and 
the extracted beam sizes at different kicker angles compared to simulation [new ref here].  
When it becomes possible to test the complete simulation solution, it is expected that there will not be perfect agreement with simulation;
for example there may be errors in the fields of beamline elements.  However, the simulation can be a tool to track down the source of
discrepancies, such as understanding the effect of the gun field on the beam symmetry.  
More importantly, the optimization results should provide significant improvement in efficiency for achieving a good operational regime.
